Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-23 cav2017/cav2017.tex
text

\subsubsection{Effect on safety specification and stability}
First consider the effect of the quantization error on safety; the state values must be computed considering the error introduced by the digital controller caused by performing the multiplication $K*x$ at low digital precision.
%, and the digital reference signal. 
%In this paper, we consider systems with a reference signal equal to zero. 
%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
%and disregarding it in the state equation~\eqref{eq:plant}.
Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ 
to to denote numbers represented with the precision of the digital controller, where $I_c$ is the number of bits used to represent the integer value in the controller and $F_c$ is the number of bits used to represent the fractional part of numbers in the controller. 
%
\begin{align*}
u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}

We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is $\delta$ away from the desired equilibrium point, see Appendix. In this paper, we are concerned with \emph{safe} controllers and therefore concerned only that the system converges to a point within the safety specification. Hence, it is sufficient to synthesise a stable controller based on infinite precision, and then verify safety.

>>>>

\subsubsection{Effect on safety specification and stability}
First consider the effect of the quantization error on safety; the state values must be computed considering the error introduced by the digital controller caused by performing the vector multiplication $Kx$ at low digital precision.
%, and the digital reference signal. 
%In this paper, we consider systems with a reference signal equal to zero. 
%the FWL effects in all operations related to the control action~\eqref{eq:controlaction} 
%and disregarding it in the state equation~\eqref{eq:plant}.
Thus, the states are computed using the following equations. We use $\mathcal{F}_{\langle I_c,F_c \rangle}$ \todo{These notations are different from those above.}
to to denote numbers represented with the precision of the digital controller, where $I_c$ is the number of bits used to represent the integer value in the controller and $F_c$ is the number of bits used to represent the fractional part of the numbers manipulated within the controller. 
%
\begin{align*}
u_{k}&=-(\mathcal{F}_{\langle I_c,F_c \rangle}(K)\cdot\mathcal{F}_{\langle I_c,F_c \rangle}(x_{k})).  
%\\ x_{k+1}&=A_d x_{k} + B_du_{k}
\end{align*}

We note that the effect on stability due to the fixed-word-length error is that the system may, instead of converging to the desired equilibrium point, converge to a point that is bounded away from the desired equilibrium point (see Appendix for details). 
In this paper, we are concerned with \emph{safe} controllers and therefore concerned only that the system converges to a point within the safety specification. Hence, it is sufficient to synthesise a stable controller based on infinite precision, and then verify safety.
